---
title: "Overview of the FARSfunctions package"
author:"Oliver Kempter"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette_FARSfunctions}
  %\VignetteEngine{rmarkdown:render}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
library(readr)
library(magrittr)
library(dplyr)
library(tidyr)
library(maps)
library(graphics)
```

This vignette gives an overview about the functions, provided in the FARSfunctions package.


##Package functions

There are five functions which comes with the FARSfunction package.

```{r, eval = FALSE}
#fars_read()
#make_filename()
#fars_read_years()
#fars_summarize_years()
#fars_map_state()
```


###fars_read

fars_read: This function is a wrapper from the read_csv function in the package readr. It reads in a single csv file (.csv or .csv.bz2) and returns a data frame. This file should be located in the same directory as the working directory.
In case the file does not exist, in error message ("file", filename, " does not exist") is printed out.

####Usage
```{r, eval = FALSE}
#fars_read(filename)
```


###make_filename

make_filename(): This function embeds the year into an existing pattern ("accident_%d.csv.bz2").

####Usage
```{r}
make_filename(2013)
make_filename(2014)
make_filename(2015)
```


###fars_read_years
fars_read_years: This function prints out lists of data.frames.
Each data frame is sorted by month and year of the motor vehicle traffic crash.
You can use a vector of years for multiple data.frames.
In case specified year can not be found, the function prints out a warning message.

####Usage
```{r, echo = FALSE}
#fars_read_years(2013)
```


###fars_summarize_years
fars_summarize_years: This function summarizes the total number of motor vehicle traffic crashes by month, for a specified year. Use a vector of multiple years to add further columns to the data frame.

####Usage
```{r, echo = FALSE}
#fars_summarize_years(c(2013, 2014, 2015))
```


###fars_map_state
fars_map_state: This function takes the state number and year as argument and maps
motor vehicle traffic crashes on this map.
In case the state number is not valid an error message is an error message is returned.

####Usage
```{r, echo = FALSE}
#fars_map_state(1, 2013)
```

```{r,echo = FALSE}
#fars_map_state(2, 2014)
```
